\documentclass[A4]{scrartcl}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subcaption}
%\usepackage[ddmmyyyyy]{datetime}

\usepackage{amsmath} % Putting text in equations...
\usepackage{color} % Colorzzzzzz
\usepackage{float} % Om pictures op de juiste plaats te krijgen met "H".


\usepackage[%
  backend=bibtex      % biber or bibtex
%,style=authoryear    % Alphabeticalsch
 ,style=numeric-comp  % numerical-compressed
 ,sorting=none        % no sorting
 ,sortcites=true      % some other example options ...
 ,block=none
 ,indexing=false
 ,citereset=none
 ,isbn=true
 ,url=true
 ,doi=true            % prints doi
 ,natbib=true         % if you need natbib functions
]{biblatex}
\bibliography{bib}

\definecolor{lbcolor}{rgb}{0.85,0.85,0.85}
\definecolor{LinkColor}{rgb}{0,0,0.5}
\lstset{language=bash,
	numbers=left,
	stepnumber=1,
	numbersep=5pt,
	numberstyle=\tiny,
	breaklines=true,
	breakautoindent=true,
	postbreak=\space,
	tabsize=2,
	basicstyle=\ttfamily\footnotesize,
	showspaces=false,
	showstringspaces=false,
	extendedchars=true,
	backgroundcolor=\color{lbcolor}
}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}


\begin{document}

\begin{titlepage}
	\begin{center}
		
		% Upper part of the page. The '~' is needed because \\
		% only works if a paragraph has started.
		\HRule \\[0.5cm]
		\textsc{\LARGE Graph 500 on the public cloud}\\[0.5cm]
		\HRule \\[0.3cm]
		
		\textsc{\large{Master System and Network Engineering - RP2}}\\[0.5cm]
		%images
		
		\vfill
		
		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushleft} \large 
				\emph{Author:}\\
				Harm Dermois\texttt{ harm.dermois@os3.nl}
			\end{flushleft}
		\end{minipage}%
		\begin{minipage}[t]{0.4\textwidth}
			\begin{flushleft} \large
				\emph{Supervisor:} \\
				Ana Lucia Varbanescu \\
				\texttt{a.l.varbanescu@uva.nl}\\				
			\end{flushleft}
		\end{minipage}
		
	\end{center}
	
	\vspace{2cm}

		
		
		\vfill
		
		% Bottom of the page
		{\large \today}
		
\end{titlepage}


\newpage



\newpage

\section*{Acknowledgments}
I would like to thank my supervisor Ana Varbanescu, for all the help and feedback she has given me. I also want to thank Ana Opresecu with the advise and help she provided with working on the cloud. Kees Verstoep for helping me with the DAS-4 and OpenNebula. Yuri Demchenko for providing a Amazon account for my experiments. Amazon Web Services help desk for their quick response to my request to increase the instance limit.

\newpage

\section*{Abstract}
	\textit{In this project the viability of the Graph 500 benchmark on the cloud has been tested. The performance one Graph 500 benchmark application has been evaluated on the DAS-4 and Amazon EC2. We found that using the cloud is competitive with super computers. We also created a model for predicting the performance of the benchmark given the resources.}

\newpage

\tableofcontents
\newpage

\section{Introduction}
\label{sec:introduction}
\input{sections/introduction.tex}


\section{Research Question}
\label{research-questions}
\input{sections/researchquestions.tex}

%\subsection{Scope}
%\label{scope}
%\input{sections/scope.tex}

\section{Background and Related Work}
\label{background}
\input{sections/background.tex}

\newpage
\subsection{Related Work}
\label{related-work}
\input{sections/relatedwork.tex}

\newpage
\section{Methodology}
\label{methodology}
\input{sections/methodology.tex}
\newpage
\section{Results}
\label{results}
\input{sections/results.tex}

\newpage
\section{Model}
\label{model}
\input{sections/model.tex}

\newpage
\section{Discussion}
\label{discussion}
\input{sections/discussion.tex}


\section{Conclusion}
\label{conclusion}
\input{sections/conclusion.tex}

\section{Future Work}
\label{future-work}
\input{sections/futurework.tex}


\newpage

\printbibliography

\newpage

\appendix

\input{sections/appendix.tex}

\end{document}
