With running the program there were some problems. The frist problem was
that the mpi version on the DAS-4 is a very old version, mpi version 1.4. This
was not compatible with the reference code. Because of this the workaround.h
needed to be adjusted. This worked out the problems which were created during compile time.
It was said that this would help out with the validation and would cause it not to hang. This
was the case for a scale till 15. At a scale of 18 or higher the problem would get stuck while
validating the first BFS. To remedy this the validation was left out, because this is the reference
code the validation of the BFS is less of a concern and the program does not run with it. The method
of removing the validation was taken from this technical paper written by Angel et al.\cite{angel2012graph}.
In this paper it is proposed that instead of dividing the time the BFS took to run by the actual visited edges,
the total number of edges is taken. This is a good proximation of the problem because of the properties
of the Kronecker graph and the edge factor which is 16(16 edges per node). This makes the graph fully connected
and the assumption that all nodes have been visited true. In the graph [GRAPJH no validation] you can see that
the graphs with and without validation differ slightly. The difference with larger scales also become smaller
because of the property of the Kronecker graph that the larger the scale the more connected the graph becomes.
%TODO need to write down the terms of kronecker and check everything.