
The goal of the project is to benchmark the Graph 500 kernels on the cloud to find a model to predict the performance of the benchmark for the chosen scale and number of nodes. To create a baseline, experiments were done on the DAS-4 and OpenNebula, before running the benchmark on the cloud. In the following sections the hardware used will be shown.
\subsubsection{Das-4}
\label{hw:das4}
The Distributed ASCI Supercomputer 4 (DAS-4) is a six-cluster wide-area distributed system designed by the Advanced School for Computing and Imagining (ASCI)\cite{das-4}. The six-clusters are the following:
\begin{itemize}
\item Vrije Univeristeit (VU)
\item Leiden Univeristeit (LU)
\item Univeristeit van Amsterdam (UvA) 
\item Technische Universiteit Delft (TUD)
\item Univeristeit van Amsterdam - The MultimediaN (UVA-MN) 
\item Astronomy institute Netherlands Institute for Radio Astronomy (ASTRON)
\end{itemize}
All computations have been done on the clusters from he VU and LU. These two clusters are chosen because the cluster of LU is not actively used. The VU cluster was used, because it has the most machine available and has an OpenNebula cluster installed on it. The specifications of the clusters can be found in table \ref{tab:das-clusters}. 

Each of the nodes in the clusters has a dual quad-core processor with a speed of 2.4 GHz. All the nodes are also connected with InfiniBand\cite{infiniband}. All nodes on the cluster have CentOS release 6.6 (Final) installed.
\begin{table}[!h]
	\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Cluster & Number of nodes  & Memory(GB) \\ \hline
VU 		& 74 (41) for all purposed	 & 24			\\ \hline
LU		& 16 & 48 \\ \hline
\end{tabular}
\end{center}
\caption{The specifications of the clusters used in this project.}
\label{tab:das-clusters}
\end{table}



\subsubsection{OpenNebula}
\label{hw:opennebula}
``OpenNebula  provides the most simple but feature-rich and flexible solution for the comprehensive management of virtualized data centers to enable private, public and hybrid IaaS clouds. OpenNebula interoperability makes cloud an evolution by leveraging existing IT assets, protecting your investments, and avoiding vendor lock-in.'' \cite{opennebula}. The version of OpenNebula(ON) installed on the VU cluster is version 3.8. The ON cluster on the DAS-4 consists of eight nodes, the specifications of these nodes are different from the other nodes in the cluster. Table \ref{tab:specs-opennebula} shows the specifications of the ON nodes. ON uses templates to define resources of the machine that needs to be created. The VMs created used the following two templates seen in Appendix[Reference].
\begin{table} [!h]
	\begin{center}
	\begin{tabular}{|l|l|l|}
		\hline
		CPU & Number of cores & RAM  \\ \hline
		Intel(R) Xeon(R) CPU E5-2620 0 2.00 GHz & 24 & 66 GB\\ \hline
	\end{tabular}
	\caption{The specifications of the OpenNebula host nodes.}
	\label{tab:specs-opennebula}
	\end{center}
\end{table}

\subsubsection{Amazon EC2 instance types}
\label{hw:Amazon}
The Amazon Elastic Compute Cloud(Amazon EC2) has many different types of instances which optimized for a specific purpose\cite{amazon-instances}. The following types have been defined:
\begin{description}
\item[T - Burstable Performance Instances] provide burst of CPU with a low baseline.
\item[M - Balanced] Well balanced in terms of memory, CPU and network resources.
\item[C -Computation Optimized] Used for computationally intensive tasks.
\item[R - Memory Optimized] Used for memory intensive tasks.
\item[G - GPU] Has a GPU.
\item[I - High I/O] Has large SSDs for fast I/O.
\item[D - Dense Storage] Has large HDD for storing a lot data.
\end{description}
From these types there are a few types which are interesting for this project, namely: M,C and R. We have chosen to use the C and R to find out if the using a computation or memory optimized instances will make a difference for \texttt{graph500\_mpi\_simple}.
These types have also different sizes and generations. The R and C type both have 5 different sizes, but the R type has only one(3) generation while the C has two. To be able to compare them the same size and generation has been chosen which is generation 3 and size large. Size ``large'' is the smallest size which can be used for this type. We chose this size, because these are the cheapest instances of these types. Also the number of CPUs is not important(see \ref{sec:openmp}), which makes using larger instances a waste of money. The specification can seen in table \ref{tab:specs-amazon} each larger size doubles the amount of resource available to the machine.

The experiments will be run in the Ireland region.

\begin{table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Type & vCPU & Mem GB & Processor \\ \hline
c3.large & 2 & 4 & Intel Xeon E5-2680 v2 (Ivy Bridge) Processors 2.80 GHz \\ \hline
r3.large & 2 & 16 & Intel Xeon E5-2670 v2 (Ivy Bridge) Processors 2.50 GHz \\ \hline
\end{tabular}
\end{center}
\caption{The specifications of the Amazon EC2 instances chosen for this project.}
\label{tab:specs-amazon}
\end{table}
